What is confining the proplyd bow shocks in Orion?

### 2016-10-21 papers/Paper1/proplyd-bowshocks.tex
Lots of improvements to section 3
Also, upgrade to the latest version of MNRAS macros: mnras.cls
Incorporate appendix into both papers

\RequirePackage{amsmath}
\documentclass[useAMS,usenatbib]{mn2e}

% The following is needed to fix the margins if using Letter-size paper
% REMOVE if your LaTeX uses A4 paper by default
\addtolength\topmargin{-1.8cm}

% Standard LaTeX packages
\usepackage[varg]{txfonts}
% \usepackage[varg]{newtxmath}
% \usepackage{newtxtext}
\usepackage{graphicx}
\usepackage{microtype}
\usepackage{xcolor}
\usepackage{fixltx2e}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{siunitx}
\usepackage{color}
\hypersetup{colorlinks=True, linkcolor=blue!50!black, citecolor=black,
  urlcolor=blue!50!black}

%% Bundled custom packages
\usepackage{aastex-compat}
\usepackage{astrojournals}

\title[Bowshock shapes]{True versus apparent shapes of astrophysical bow shocks}

\newcommand\AddressCRyA{Instituto de Radioastronom\'{\i}a y Astrof\'{\i}sica,
  Universidad Nacional Aut\'onoma de M\'exico, Apartado Postal 3-72,
  58090 Morelia, Michoac\'an, M\'exico}
\author[Tarango Yong \& Henney]{
  Jorge A. Tarango Yong \& William J. Henney\\
  \AddressCRyA
}
\begin{document}
\maketitle
\begin{abstract}
  We develop a general framework for the effects of viewing angle on
  the apparent shape of a limb-brightened, cylindrically symmetric
  curved shock (bow shock).  
\end{abstract}

\input{sec-intro}
\input{sec-generic-model}
\input{sec-projection}
\input{sec-conic}
\input{sec-application}
\input{sec-conclusions}

%% TODO Investigate newer versions of BST file from
%% https://github.com/timj/mn2e-bst
\bibliographystyle{mn2e}
%% All references should be put in the BibTeX file bowshocks-biblio.bib
\bibliography{bowshocks-biblio}

>>>>

\RequirePackage{amsmath}
\documentclass[useAMS, usenatbib]{mnras}

% The following is needed to fix the margins if using Letter-size paper
% REMOVE if your LaTeX uses A4 paper by default
%\addtolength\topmargin{-1.8cm}

% Standard LaTeX packages
% \usepackage[varg]{txfonts}
\usepackage[varg]{newtxmath}
\usepackage{newtxtext}
\usepackage{graphicx}
\usepackage{microtype}
\usepackage{xcolor}
\usepackage{fixltx2e}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{siunitx}
\usepackage{color}
\usepackage{appendix}
\hypersetup{colorlinks=True, linkcolor=blue!50!black, citecolor=black,
  urlcolor=blue!50!black}

%% Bold italic
\newcommand\hmmax{0}            % we don't need heavy fonts
\newcommand\bmmax{1}            % reduce use of math alphabets for bold
\usepackage{bm}

%% Bundled custom packages
\usepackage{aastex-compat}
%\usepackage{astrojournals}

\title[Proplyd bowshocks]{What is confining the proplyd bow shocks in Orion?}

\newcommand\AddressCRyA{Instituto de Radioastronom\'{\i}a y Astrof\'{\i}sica,
  Universidad Nacional Aut\'onoma de M\'exico, Apartado Postal 3-72,
  58090 Morelia, Michoac\'an, M\'exico}
\author[Tarango Yong \& Henney]{
  Jorge A. Tarango Yong \& William J. Henney\\
  \AddressCRyA
}
\begin{document}
\maketitle
\begin{abstract}
  We analyze the projected shapes of bowshocks associated with
  photoevaporating disks (proplyds) in the inner Orion Nebula.  We
  show that the photoevaporation flows must be anisotropic in order to
  reproduce the observed shapes.  The stagnation pressures of the
  shocked shells within 0.02~pc of the dominant high-mass star are
  consistent with an interaction with its unshocked stellar wind, but
  the more distant shells require a confining pressure that is an
  order of magnitude higher than can be provided by the unmodified
  wind.  We show that these outer objects may be proplyds that are
  interacting with the conical wake generated by the wind-wind
  interaction in the inner proplyds. 
\end{abstract}

\newcommand\thC{\(\theta^1\)\,Ori~C}
\defcitealias{Canto:1996}{CRW}
\newcommand\CRW{\citetalias{Canto:1996}}

\input{sec-intro-proplyd}
\input{sec-application}
\input{sec-conclusions-proplyd}

\bibliographystyle{mnras}
%% All references should be put in the BibTeX file bowshocks-biblio.bib
\bibliography{bowshocks-biblio}

### 2016-10-21 papers/Paper1/sec-conic.tex
Enhance appareance of figure 6 using seaborn
Incorporate appendix into both papers

%Instead of the excentricity, we utilize the parameter $\theta_c$ to characterize the different curves, where
%$\tan\theta_c = \frac{b}{a}$,  $b$ and $a$ are the typical parameters of conics. A positive value for $\theta_c$ indicates that the given curve is a closed one, i.e
%an ellipse, while a negative value indicates that is an hyperbola. %Insert figures if neccesary  
\begin{figure}
\setlength\tabcolsep{0pt}
\begin{tabular}{cc}
\includegraphics[height=0.54\linewidth, trim=30 0 30 0, clip]{ellipse_py_lab} &
\includegraphics[height=0.54\linewidth, trim=60 0 70 0, clip]{hyperbola_py_lab}
\end{tabular}
\label{fig:conics}
\caption{Schematic representation of conic like bowshocks: A) Ellipse and B) Hyperbola The center of the conic is located at a distance $x_0=R_0-a$ from the origin at the $x$ axis. 
The radius of curvature at the axis is $R_c$, and $R_{90}$ is t he radius of the conic in the perpendicular direction to $R_0$.
}
\end{figure}
\begin{figure}
\includegraphics[width=\linewidth]{conic1}
\caption{Example of a family of conic sections, all with the same
  radius of curvature at their apex (marked by white dot) on the
  \(x\)~axis: \(R_c = 2 R_0\). The parameter
  $\theta_c = \pm \tan^{-1} b/a$ describes the family, with negative
  values corresponding to hyperbolae.}
\label{fig:conics-family}
\end{figure}

Due to the similarities between the parametrization of the ellipse and the hyperbola, we can do the following parametrization:
\begin{align}
x = a\Cos(t)-x_0 \label{eq:par-x}\\ 
y = b\Sin(t) \label{eq:par-y}
\end{align}
where:
\begin{align}
\Cos(t) = \left\lbrace \begin{array}{c}
\cos t ~\mathrm{if~ellipse} \\
\cosh t ~\mathrm{if~hyperbola}
\end{array}\right.\\
\Sin(t) = \left\lbrace \begin{array}{c}
\sin t ~\mathrm{if~ellipse} \\
\sinh t ~\mathrm{if~hyperbola}
\end{array}\right. \\
-\pi < t < \pi \\
R_0 = a - x_0 \\
a<0 ~ \mathrm{for~hyperbola}
\end{align}
We have set a whole family of curves with a singular parameter denoted as $\tan\theta_c \equiv \frac{b}{a}$. Positive values of this parameter describe closed curves
(i.e. ellipses) and the negative ones describe open curves (i.e. hyperbolas). Particular cases are $\theta_c =\frac{\pi}{4}$, which describes a circle and $\theta_c=0$, which describes
a parabola.
To determine uniquely a given conic in terms of measurable quantities, we use the set of characteristic radii $(R_0,R_c,R_{90})$ in such way the conic parameters $(a,b,\theta_c)$
could be derived from the former. The transformation between the conic parameters and the characteristic radii are given by:
\begin{align}
R_c &= \frac{b^2}{a} \label{eq:Rc-conic}\\ 
R_{90} &= b\left[\pm\left(1 - \frac{(R_0-a)^2}{a^2}\right)\right]^{1/2}\label{eq:r90-conic}
\end{align}
In (\ref{eq:r90-conic}), the positive sign correspond to an elliptic quadric, while the negative sign to an hyperbolic quadric. The inverse transformation of (\ref{eq:Rc-conic})
and (\ref{eq:r90-conic}) is given by:
\begin{align}
\frac{a}{R_0} &= \frac{A}{2A-B^2} \label{eq:a-conic}\\
\frac{|b|}{R_0} &= \frac{A}{\left|2A-B^2\right|^{1/2}}\\
\tan\theta_c &= \frac{2A-B^2}{\left|B^2 - 2A\right|^{1/2}} \label{eq:thc-conic} \\
\mathrm{where:~}& B\equiv \frac{R_{90}}{R_0} \\
A \equiv \frac{R_c}{R_0}
\end{align}

@@

Once the parametrization is done, we can find the apparent shape of
the shell in the observer's frame, following the procedure explained
in section \ref{sec:projection}.  First of all, the intrinsic 3D shape of the shell is given by:
\begin{align}
x = a\Cos(t)-x_0 \\ 
y = b\Sin(t)\cos\phi \\
z =  b\Sin(t)\sin\phi
\end{align}
The azimutal angle where the line of sight is tangent to the shell is given by equation (\ref{eq:tanphi}) and (\ref{eq:alpha}), then:
\begin{align}
\sin\phi_t &= \frac{b}{a}\tan i\Cot(t) 
\end{align}
where:
\begin{align}
\Cot(t) = \left\lbrace \begin{array}{c}
\cot t ~\mathrm{if~ellipse} \\
-\coth t ~\mathrm{if~hyperbola}
\end{array}\right.
\end{align}

We could work in another frame where the origin is located at the conic's center: $(X,Y)$, where $X=x-X_0$ and $Y=y$.
In this frame,  we use the transformations (\ref{eq:Trans})  to obtain the apparent shape of the shell:
\begin{align}
X' = \frac{\Cos(t)}{a\cos i}\left(a^2\cos^2 i \pm b^2\sin^2 i\right)  \label{eq:conic-projected-x}\\
Y'= b\Sin(t)\left(1-\frac{b^2}{a^2}\tan^2 i\Cot^2(t)\right)^{1/2}
\label{eq:conic-projected-y}
\end{align}

We must show that the apparent shape of the shell in the observer's frame is still the same conic. To do that, we can write equations
(\ref{eq:conic-projected-x}) and (\ref{eq:conic-projected-y}) as follows:
\begin{align}
X' = a'\Cos t' \label{eq:conic-projected-x-2} \\
Y' = b'\Sin t' \label{eq:conic-projected-y-2} . 
\end{align}

Comparing, (\ref{eq:conic-projected-x}), (\ref{eq:conic-projected-x-2}), (\ref{eq:conic-projected-y}) and (\ref{eq:conic-projected-y-2}) we find that
\begin{align}
a' = \left(a^2\cos^2 i \pm b^2\sin^2 i\right)^{1/2} \\
\Cos(t') = \frac{a'\Cos(t)}{a\cos i} \\
b' = b
\end{align} 
Which proves that effectively the projection of a given conic is the same conic. With this knowledge, we can obtain the characteristic radii in
the observer's frame.
\begin{align}
D' = D\cos i \\
R'_0 = a' - (a-R_0)\cos i \\
R'_0 = \left(a^2\cos^2 i \pm b^2\sin^2 i\right)^{1/2}  - (a-R_0)\cos i
\end{align}

>>>>

%Instead of the excentricity, we utilize the parameter $\theta_c$ to characterize the different curves, where
%$\tan\theta_c = \frac{b}{a}$,  $b$ and $a$ are the typical parameters of conics. A positive value for $\theta_c$ indicates that the given curve is a closed one, i.e
%an ellipse, while a negative value indicates that is an hyperbola. %Insert figures if neccesary  
\begin{figure}
\setlength\tabcolsep{0pt}
\begin{tabular}{cc}
\includegraphics[height=0.54\linewidth, trim=30 0 30 0, clip]{ellipse_py} &
\includegraphics[height=0.54\linewidth, trim=60 0 70 0, clip]{hyperbola_py}
\end{tabular}
\label{fig:conics}
\caption{Schematic representation of conic like bowshocks: A) Ellipse and B) Hyperbola The center of the conic is located at a distance $x_0=R_0-a$ from the origin at the $x$ axis. 
The radius of curvature at the axis is $R_c$, and $R_{90}$ is t he radius of the conic in the perpendicular direction to $R_0$.
}
\end{figure}
\begin{figure}
\includegraphics[width=\linewidth]{conic1}
\caption{Example of a family of conic sections, all with the same
  radius of curvature at their apex (marked by white dot) on the
  \(x\)~axis: \(R_c = 2 R_0\). The parameter
  $\theta_c = \pm \tan^{-1} b/a$ describes the family, with negative
  values corresponding to hyperbolae.}
\label{fig:conics-family}
\end{figure}

Due to the similarities between the parametrization of the ellipse and the hyperbola, we can do the following parametrization:
\begin{align}
x &= a\Cos(t)-x_0 \label{eq:par-x}\\ 
y &= b\Sin(t) \label{eq:par-y}
\end{align}
where:
\begin{align}
\Cos(t) &= \left\lbrace \begin{array}{c}
\cos t ~\mathrm{if~ellipse} \\
\cosh t ~\mathrm{if~hyperbola}
\end{array}\right.\\
\Sin(t) &= \left\lbrace \begin{array}{c}
\sin t ~\mathrm{if~ellipse} \\
\sinh t ~\mathrm{if~hyperbola}
\end{array}\right. \\
-\pi < t < \pi \\
R_0 &= a - x_0 \\
a<0 ~ \mathrm{for~hyperbola}
\end{align}
We have set a whole family of curves with a singular parameter denoted as $\tan\theta_c \equiv \frac{b}{a}$. Positive values of this parameter describe closed curves
(i.e. ellipses) and the negative ones describe open curves (i.e. hyperbolas). Particular cases are $\theta_c =\frac{\pi}{4}$, which describes a circle and $\theta_c=0$, which describes
a parabola.
To determine uniquely a given conic in terms of measurable quantities, we use the set of characteristic radii $(R_0,R_c,R_{90})$ in such way the conic parameters $(a,b,\theta_c)$
could be derived from the former. The transformation between the conic parameters and the characteristic radii are given by:
\begin{align}
R_c &= \frac{b^2}{a} \label{eq:Rc-conic}\\ 
R_{90} &= b\left[\pm\left(1 - \frac{(R_0-a)^2}{a^2}\right)\right]^{1/2}\label{eq:r90-conic}
\end{align}
In (\ref{eq:r90-conic}), the positive sign correspond to an elliptic quadric, while the negative sign to an hyperbolic quadric. The inverse transformation of (\ref{eq:Rc-conic})
and (\ref{eq:r90-conic}) is given by:
\begin{align}
\frac{a}{R_0} &= \frac{A}{2A-B^2} \label{eq:a-conic}\\
\frac{|b|}{R_0} &= \frac{A}{\left|2A-B^2\right|^{1/2}}\\
\tan\theta_c &= \frac{2A-B^2}{\left|B^2 - 2A\right|^{1/2}} \label{eq:thc-conic} \\
\mathrm{where:~} B &\equiv \frac{R_{90}}{R_0} \\
A &\equiv \frac{R_c}{R_0}
\end{align}

@@

Once the parametrization is done, we can find the apparent shape of
the shell in the observer's frame, following the procedure explained
in section \ref{sec:projection}.  First of all, the intrinsic 3D shape of the shell is given by:
\begin{align}
x &= a\Cos(t)-x_0 \\ 
y &= b\Sin(t)\cos\phi \\
z &=  b\Sin(t)\sin\phi
\end{align}
The azimutal angle where the line of sight is tangent to the shell is given by equation (\ref{eq:tanphi}) and (\ref{eq:alpha}), then:
\begin{align}
\sin\phi_t &= \frac{b}{a}\tan i\Cot(t) 
\end{align}
where:
\begin{align}
\Cot(t) = \left\lbrace \begin{array}{c}
\cot t ~\mathrm{if~ellipse} \\
-\coth t ~\mathrm{if~hyperbola}
\end{array}\right.
\end{align}

We could work in another frame where the origin is located at the conic's center: $(X,Y)$, where $X=x-X_0$ and $Y=y$.
In this frame,  we use the transformations (\ref{eq:Trans})  to obtain the apparent shape of the shell:
\begin{align}
X' &= \frac{\Cos(t)}{a\cos i}\left(a^2\cos^2 i \pm b^2\sin^2 i\right)  \label{eq:conic-projected-x}\\
Y' &= b\Sin(t)\left(1-\frac{b^2}{a^2}\tan^2 i\Cot^2(t)\right)^{1/2}
\label{eq:conic-projected-y}
\end{align}

We must show that the apparent shape of the shell in the observer's frame is still the same conic. To do that, we can write equations
(\ref{eq:conic-projected-x}) and (\ref{eq:conic-projected-y}) as follows:
\begin{align}
X' &= a'\Cos t' \label{eq:conic-projected-x-2} \\
Y' &= b'\Sin t' \label{eq:conic-projected-y-2} . 
\end{align}

Comparing, (\ref{eq:conic-projected-x}), (\ref{eq:conic-projected-x-2}), (\ref{eq:conic-projected-y}) and (\ref{eq:conic-projected-y-2}) we find that
\begin{align}
a' &= \left(a^2\cos^2 i \pm b^2\sin^2 i\right)^{1/2} \\
\Cos(t') &= \frac{a'\Cos(t)}{a\cos i} \\
b' &= b
\end{align} 
Which proves that effectively the projection of a given conic is the same conic. With this knowledge, we can obtain the characteristic radii in
the observer's frame.
\begin{align}
D' &= D\cos i \\
R'_0 &= a' - (a-R_0)\cos i \\
R'_0 &= \left(a^2\cos^2 i \pm b^2\sin^2 i\right)^{1/2}  - (a-R_0)\cos i
\end{align}

### 2016-10-21 papers/Paper1/sec-projection.tex
Incorporate appendix into both papers

%Note: I'm aware that some of this material should be moved to an appendix, but I think it will be a future edition.
\subsection{Frames of reference}

@@

\subsection{Characteristic radii}
\label{sec:characteristic-radii}
\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/characteristic-radii}
  \caption{Characteristic radii in the body frame.}
  \label{fig:characteristic-radii}
\end{figure}

\subsection{Unit vectors normal and tangential to the surface}
\label{sec:unit-vectors-normal}
\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/bowshock-unit-vectors}
  \caption{Unit vectors in the body frame that are normal and
    tangential to the surface \(R(\theta)\) in a plane of constant
    azimuth, \(\phi\).}
  \label{fig:unitvec}
\end{figure}
We define unit vectors \(\uvec{n}, \uvec{t}\), such that \(\uvec{n}\) is normal to the surface, while \(\uvec{t}\) is tangent to the surface in a plane of constant \(\phi\). For \(\phi = 0\) the surface lies in the \(xy\) plane and it is straightforward to show (Fig.~\ref{fig:unitvec}) that in this case the unit vectors are given by 
\begin{equation}
  \label{eq:uvec-phi0}
  \uvec{t}_0 =
  \begin{Vector}
    -\cos\alpha \\ \sin\alpha \\ 0
  \end{Vector}
  \quad \mathrm{and} \quad
  \uvec{n}_0 =
  \begin{Vector}
    \sin\alpha \\ \cos\alpha \\ 0
  \end{Vector}, 
\end{equation}
where
\begin{equation}
  \label{eq:alpha}
  \tan\alpha = -\left.\frac{dy}{dx}\right\vert_{R(\theta)} 
  = \frac{1 + \omega \tan\theta}{\tan\theta - \omega}
\end{equation}
and 
\begin{equation}
  \label{eq:omega}
  \omega(\theta) = \frac{1}{R} \frac{dR}{d\theta} . 
\end{equation}
For general \(\phi\), \(\uvec{n}\) and \(\uvec{t}\) can be found by rotating equations~(\ref{eq:uvec-phi0}) around the \(x\)-axis, which can then be converted to the observer frame by use of equation~(\ref{eq:Trans}) to give
\begin{gather}
  \label{eq:nprime}
  \begin{split}
    \uvec{n}' = & \frac{1}{(1+\omega^2)^{1/2}} \\
    & \times 
      \begin{Vector}
        (\cos\theta+\omega\sin\theta)\cos i 
        - (\sin\theta-\omega\cos\theta) \sin i \sin\phi\\
        (\sin\theta-\omega\cos\theta)\cos\phi \\
        (\cos\theta+\omega\sin\theta)\sin i 
        + (\sin\theta-\omega\cos\theta)\sin\phi\cos i
      \end{Vector}\\
  \end{split}\\
  \label{eq:tprime}
  \begin{split}
    \uvec{t}' = & \frac{1}{(1+\omega^2)^{1/2}} \\
    & \times 
      \begin{Vector}
        -(\sin\theta-\omega\cos\theta)\cos i
        - (\cos\theta+\omega\sin\theta)\sin\phi\sin i \\
        (\cos\theta+\omega\sin\theta)\cos\phi \\
        -(\cos\theta+\omega\sin\theta)\sin i 
        + (\sin\theta-\omega\cos\theta)\sin\phi\cos i
      \end{Vector}
  \end{split}
  \end{gather}

@@

@@

The boundary on the plane of the sky of the projected surface is the
locus of those lines of sight that graze the surface tangentially.
This corresponds to a curved line on the surface itself, which we
denote the \textit{tangent line}, and which is defined by the
condition 
\begin{equation}
  \label{eq:tangent-line-condition}
  \uvec{n}'\cdot \uvec{z}' = 0.
\end{equation}
We denote by \(\phi\T\) that value of $\phi$ that satisfies this
relation for a given inclination, \(i\), and polar angle, \(\theta\):
\begin{equation}
\sin\phi\T = \tan i\tan\alpha = \tan i \frac{1+\omega\tan\theta}{\omega-\tan\theta}
\label{eq:tanphi}
\end{equation}
From equations~(\ref{eq:body-frame}, \ref{eq:Trans}) it follows that
the observer-frame coordinates of the tangent line are given by
\begin{equation}
\left(\begin{array}{c}
x'\T \\ y'\T \\ z'\T
\end{array}\right)= R(\theta)\left(\begin{array}{c}
\cos\theta\cos i - \sin\theta\sin\phi\T \sin i \\
\sin\theta(1-\sin^2\phi\T)^{1/2} \\
\cos\theta\sin i +\sin\theta\sin\phi\T\cos i
\end{array}\right).
\label{eq:tangential}
\end{equation} 
Note that, in general, \(z'\T\) is not a linear function of \(x'\T\)
and \(y'\T\), so that the tangent line is not a plane curve.

>>>>

%Note: I'm aware that some of this material should be moved to an appendix, but I think it will be a future edition.
\subsection{Frames of reference}
\label{sec:ref-frames}

@@

%\subsection{Characteristic radii}
%\label{sec:characteristic-radii}
\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/characteristic-radii}
  \caption{Characteristic radii in the body frame.}
  \label{fig:characteristic-radii}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/bowshock-unit-vectors}
  \caption{Unit vectors in the body frame that are normal and
    tangential to the surface \(R(\theta)\) in a plane of constant
    azimuth, \(\phi\).}
  \label{fig:unitvec}
\end{figure}

@@

The boundary on the plane of the sky of the projected surface is the
locus of those lines of sight that graze the surface tangentially.
This corresponds to a curved line on the surface itself, which we
denote the \textit{tangent line}, and which is defined by the
condition  
\begin{equation}
  \label{eq:tangent-line-condition}
  \uvec{n}'\cdot \uvec{z}' = 0.
\end{equation}
See appendix \ref{app:unit-vectors-normal} for more information.

We denote by \(\phi\T\) that value of $\phi$ that satisfies this
relation for a given inclination, \(i\), and polar angle, \(\theta\):
\begin{equation}
\sin\phi\T = \tan i\tan\alpha = \tan i \frac{1+\omega\tan\theta}{\omega-\tan\theta}
\label{eq:tanphi}
\end{equation}
From equations~(\ref{eq:body-frame}, \ref{eq:Trans}) it follows that
the observer-frame coordinates of the tangent line are given by
\begin{equation}
\left(\begin{array}{c}
x'\T \\ y'\T \\ z'\T
\end{array}\right)= R(\theta)\left(\begin{array}{c}
\cos\theta\cos i - \sin\theta\sin\phi\T \sin i \\
\sin\theta(1-\sin^2\phi\T)^{1/2} \\
\cos\theta\sin i +\sin\theta\sin\phi\T\cos i
\end{array}\right).
\label{eq:tangential}
\end{equation} 
Note that, in general, \(z'\T\) is not a linear function of \(x'\T\)
and \(y'\T\), so that the tangent line is not a plane curve.
